---
title: "542Regression2"
author: "Group 4"
data: "3/8/2021"
output: word_document
---

Hypothesis 2

After our group meeting, we decided to have 2 hypotheses for this project. This is a document for our second hypothesis

Read input files from Github

Import our merged data by using the raw link, and named the data set as "fromPy"

```{r}
link="https://raw.githubusercontent.com/Public-Policy-COVID/students_merge/main/Merged_data.csv"
fromPy=read.csv(link, header = T)
row.names(fromPy)=NULL
```

Verifying the data structure by using the following code
To understand the type of our variables. We can change their types in future clustering or regression.

```{r}
# verifying data structure
str(fromPy,width = 50,strict.width='cut')
```

Convert integer variables to decimal variables
This step is not necessary, as integer variables are also numeric variables. It wouldn't influence our regression. Adding it in this document is to keep the variable structure constant in our analysis.

```{r}
fromPy$Deaths_COVID <- as.numeric(fromPy$Deaths_COVID) 
fromPy$Deaths_total <- as.numeric(fromPy$Deaths_total)
str(fromPy,width = 50,strict.width='cut')
```

Summary of the data set
To understand the basic information of each variable. Such as the minimum, maximum, median, mean, etc.

```{r}
summary(fromPy)
```

Test the hypothesis

State the second hypothesis, and name it "hypo2"
1. hypo2 = hypothesis 2: state with higher Deaths_COVID number has more Number_of_beds in hospitals.
2. Besides that, we think the hospital beds would be correlated with the total population, suggesting county with more population would have more beds.
3. What's more, we also want to know if race variables are significant in this analysis, thereby we added all race variables in this regression to check their relationship with the number of beds.

```{r}
hypo2=formula(Number_of_beds~ Deaths_COVID+total_population+black_total_pct+aian_total_pct+asian_total_pct+nhopi_total_pct+multiracial_total_pct)
```

Using (glm) code to compute the regression model, which stands for 'Generalized Linear Models'

```{r}
gauss2=glm(hypo2,
           data = fromPy,
           family = 'gaussian')
```

See the result of our regression
By using code (summary), we are able to check the result of our regression.

```{r}
summary(gauss2)
```

RESULTS:
Based on the results of this regression, we can tell that variable 'Deaths_COVID', 'total_population', and 'asian_total_pct' is statistically significantly correlated with our dependent variable 'Number_of_beds' at 99% confidence interval. This suggests:
1. For each county, with a 1 case increase in COVID death, there will be a 1.31 increase in the number of hospital beds.
2. For each county, with 1 person increase in the total population, there will be a 1.55 increase in the number of beds in the number of hospital beds.
3. For each county, with a 1 percent increase in the proportion of the Asian population, there will be a 3.18 increase in the number of hospital beds.


Get the R square of this regression
R square can tell us the percentage of the response variable variation that is explained by our model. This step is to check whether this regression is an effective model. Normally, the higher the R-squared, the better the model fits our data.

```{r}


library(rsq)
rsq(gauss2, adj = T)
```

Summary plots

Plotting the coefficient estimates. We need to load the required package 'ggplot2' for it.

```{r}
library(dotwhisker)
dwplot(gauss2,by_2sd = F)
```

Plots for margins of each independent variable. We need to use the margins library package.

Margin plot for number of death for COVID variable

```{r}
library(margins)

cplot(gauss2,'Deaths_COVID')
```

Margin plot for total population variable

```{r}
cplot(gauss2,'total_population')
```

Margin plot for the percentage of Black population variable

```{r}
cplot(gauss2,'black_total_pct')
```

Margin plot for the percentage of American Indian or Alaska Native population variable

```{r}
cplot(gauss2,'aian_total_pct')
```

Margin plot for the percentage of Asian population variable

```{r}
cplot(gauss2,'asian_total_pct')
```

Margin plot for the percentage of Native Hawaiian and Other Pacific Islanders population variable

```{r}
cplot(gauss2,'nhopi_total_pct')
```

Margin plot for the percentage of Multiracial population variable

```{r}
cplot(gauss2,'multiracial_total_pct')
```

Plot the ineraction between the independent variables.

```{r}
persp(gauss2)
```

